\section{Appendix A}
\label{sec:appa}
In this appendix we evaluate how much time we have spent on realizing this project. 
For this we have defined 7 metrics. 
\emph{Total-time} , determines the amount of time for completing this project. 
\emph{Think-time}, reflects the time it took too figure out how to solve WantCloud BV’s problem. 
\emph{Dev-time},  rates the amount of time it took to code and setup the system. 
\emph{Xp-time} is the time taken by conducting experiments. 
Evaluating the results gathered from the experiments is reflected with the metric \emph{analysis-time}. 
The time taken by writing this report is represented by \emph{write-time}. 
The time it took for every  activity that cannot be accounted for in the aforementioned 6 metrics and which does facilitate progress of the project is reflected by the \emph{wasted-time}.  


Furthermore we define three metrics for each experiment. 
\emph{Total-time} is the time it took to conduct the experiments. 
The amount of time to create the experiment is reflected by \emph{dev-time}. 
\emph{Setup-time} accounts for making the environment suitable to conduct the experiment.



Table \ref{tab:ovtime} presents the time spend on the project. Whereas Table \ref{tab:exp1time}, Table \ref{tab:exp2time} and Table \ref{tab:exp3time} 
represent the time spend on the individual experiment, respectively Experiment 1, Experiment 2 and Experiment 3 conducted in Section \ref{sec:exp}.
Taken into account that at the start of the project we lacked sufficient knowledge of Python the overall (\emph{total-time}) of Table \ref{tab:ovtime} is higher than anticipated.
When conducting experiment 1 we ran in to the limititation that the micro instances have. We wrongfully assumed that there was something wrong with our cloud based system. 
Which in turn resulted in debugging the system and caused the excessive amount of time spend on Experiment 1.       
	\begin{table} 
 		\begin{center}
   			\begin{tabular}{ | l | l |}
    			\hline \textbf{Metric} & \textbf{Hour} \\ \hline
    			\emph{total-time} & 133  \\ \hline
    			\emph{think-time} & 8  \\ \hline
    			\emph{dev-time} & 65 \\ \hline
    			\emph{xp-time} & 32 \\ \hline
    			\emph{analysis-time} & 12 \\ \hline
    			\emph{write-time} & 12 \\ \hline
    			\emph{wasted-time} & 4 \\ \hline
    		\end{tabular}
			\caption{Time spend on project}
			\label{tab:ovtime}
  		\end{center}
	\end{table}
	\begin{table}
\centering
\makebox[0pt][c]{\parbox{1.2\textwidth}{
    \begin{minipage}[b]{0.32\hsize}\centering
        \begin{tabular}{ | c | c |}
           \hline
           \textbf{Metric} & \textbf{Hour} \\ \hline
           \emph{total-time} 14 \\ \hline
           \emph{dev-time} & 6 \\ \hline
           \emph{setup-time} 8 \\ \hline
        \end{tabular}
        \caption{Time spend on experiment 1}
        \label{tab:exp1time}
    \end{minipage}
    \hfill
    \begin{minipage}[b]{0.32\hsize}\centering
        \begin{tabular}{ | c | c |}
           \hline
           \textbf{Metric} & \textbf{Hour} \\ \hline
           \emph{total-time} & 7 \\ \hline
           \emph{dev-time} & 0.5 \\ \hline
           \emph{setup-time} & 2 \\ \hline
        \end{tabular}
        \caption{Time spend on experiment 2}
        \label{tab:exp2time}
    \end{minipage}
    \hfill
    \begin{minipage}[b]{0.32\hsize}\centering
        \begin{tabular}{ | c | c |}
           \hline
		   \textbf{Metric} & \textbf{Hour} \\ \hline
           \emph{total-time} & 11 \\ \hline
           \emph{dev-time} & 6 \\ \hline
           \emph{setup-time} & 5 \\ \hline
        \end{tabular}
        \caption{Time spend on experiment 3}
        \label{tab:exp3time}
    \end{minipage}
}}
\end{table}